---
title: "First Circuit Criminal Division Reports"
date-modified: last-modified
editor: visual
server: shiny

format:
  html:
    toc: true
    toc-depth: 2
    toc-expand: 1
    toc-location: left
    grid:
      sidebar-width: 200px
      body-width: 1500px
      margin-width: 50px
      gutter-width: 1.5rem
    max-width: 1600px
    theme:
      light: default
---

```{r}
#| warning: false
#| echo: false
#| context: data

library(lubridate)
library(stringr)

#Note to Adam: toggle this variable for Charge vs Case, it works in the markdown headings.
title <- "Charge"

#set constants
pending_RDS <- "2026-04-14" #date R script was run, not date Crystal Report was run

#to set x-axis range on plots
monthSelector <- '05'
yearSelector <- '2026'

#set the date in the title, might not be necessary if header has modified date
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_.*csv$")
run_dates_dispo <- str_extract(csv_dispo_list, "[0-9]{4}-[0-9]{2}-[0-9]{2}")
run_dates_dispo <- run_dates_dispo[!is.na(run_dates_dispo)]
title_date <- as.Date(max(run_dates_dispo))

#No need to touch these until 2025/01/01 -> at that time, reconfigure x-axis values for rangeslider and rangeselector to match FTA dash
#set plot range and data cutoffs----
cutoffDate <- paste0(yearSelector,'-',monthSelector,'-02')
#plots started to get crowded as new data accumulated, so control the initial range and let user pan/slide the x-axis to see older data
plotStartRange <- as.Date(cutoffDate)-lubridate::years(1) #for plots, look back one year from current month
# plotStartRange <- as.Date('2022-01-01') #for plots, look back to YTD
plotEndRange <- as.Date(cutoffDate) %m+% months(1) #for plots, look ahead one month so data isn't right up against edge of plot; #adding one month -> h/t: https://stackoverflow.com/questions/14169620/add-a-month-to-a-date
```

# `r title` Dispositions as of Trial Week (`r title_date`)

## Weekly `r title` Disposition Table

The table below shows the number of dispositions by disposition type across each criminal division in the First Circuit, Circuit Court. Use the drop down to look at historical weekly reports.

-   **Deferrals encompass DAG, DNC, and CDS dispositions. All deferrals counted here are pending.**
-   **Dismissals encompass DSM, DPJ, and DWO dispositions.**
-   **The Disposed column refers to the number of `r title`s disposed that week.**
-   **The Awaiting column refers to the number of `r title`s that either are awaiting a disposition or need to be addressed.**

```{r}
#| echo: false
#| warning: false
#| message: false
library(dplyr)
library(stringr)
library(shiny)
library(htmltools)
library(DT)
library(dplyr)
library(kableExtra)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_charge_stats_1C_trial_week_.*csv$")
run_dates_dispo <- str_extract(csv_dispo_list, "[0-9]{4}-[0-9]{2}-[0-9]{2}")
run_dates_aggregate <- str_extract(csv_dispo_list, "Aggregate")
run_dates_dispo <- append(run_dates_dispo,run_dates_aggregate)
run_dates_dispo <- run_dates_dispo[!is.na(run_dates_dispo)]

# pending_trial_list <- lapply(paste0("../pending_trials/", csv_list), read.csv)

selectizeInput(inputId = "selectWeekDispo_Case",
               label = "Select a report:",
               choices = rev(run_dates_dispo), 
               selected = TRUE
               )

#removes shiny error messages
tags$style(type="text/css",
  ".shiny-output-error { visibility: hidden; }",
  ".shiny-output-error:before { visibility: hidden; }"
) 

tags$div(class = "callout callout-style-default callout-warning callout-titled",
  tags$div(class = "callout-header",
    tags$div(class = "callout-icon-container",
      tags$i(class = "callout-icon")
    ),
    tags$div(class = "callout-title-container flex-fill", "Warning")
  ),
  tags$div(class = "callout-body-container callout-body",
    tags$p("When comparing dispositions reports, proceed with caution. The meaning of the category labels across the columns has changed over time with the rollout of data entry guidelines. The implementation of the new disposition categories happened on January 1st, 2026.")
  )
)

tableOutput("charge_dispo_table2")

#attempt to add download button using just shiny widgets to save table displayed with Kable
# downloadButton(outputId = "saveCSV", label = "CSV")

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(kableExtra)
library(DT)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
charge_dispo_table <- reactive({
    csv_selected <- list.files("WeeklyData/", pattern = paste0("^dispo_charge_stats_1C_trial_week_", input$selectWeekDispo_Case,".*?csv$"))
  dispo_charge_table_full <- read.csv(file = paste0("WeeklyData/", csv_selected))
})

  output$charge_dispo_table2 <- function(){
      charge_dispo_table() %>% rename(
        `Disposed(%)` = Disposed...,
        `Awaiting(%)` = Awaiting...) %>% 
    kable() %>% 
      kable_styling("striped","hover", font_size = 14) %>% 
      row_spec(12, bold = T) %>% 
    column_spec(16, bold = T, background = "lightgreen") %>% 
    column_spec(17, bold = T, background = "red") %>% 
    column_spec(18, bold = T)
    }

# render DT if they want the functionality of saving to csv, excel, copying
  
#  output$charge_dispo_table <- renderDT(
#  charge_dispo_trial_table(), 
#  rownames = F,
#  colnames = c("Judge\n","Division","COP","ACQJ","ACQB","GLTJ","GLTW", "Deferrals","Dismissals","DPJ48","DWO48","NPQ", "RMD", "AQRI", "MISC", "Disposed","Awaiting", "Total", "Disposed(%)", "Awaiting(%)"),
#    extensions = c("Buttons", "FixedColumns", "FixedHeader"),
#    options = list(
#      pageLength = 15,
      # lengthMenu = c(15, 25, 50),
      # scrollY = "600px", #this was creating some weird behavior in which the column heads of previous table were partially appearing
#      scrollX = TRUE,
      #add buttons, and specifying dom
      #https://stackoverflow.com/questions/50039186/add-download-buttons-in-dtrenderdatatable
      #https://stackoverflow.com/questions/50043152/r-shiny-how-to-add-pagination-in-dtrenderdatatable
      # dom = 'Bfrtip',
#      dom = 'tB',
#      buttons = c('copy','csv','excel','pdf'),
#      fixedColumns = list(leftColumns = 1), # Freeze first column
#      fixedHeader = list(header = T, footer = T) #not sure this works
      # h/t: customize font size of column heads: https://github.com/rstudio/DT/issues/783
      # headerCallback = DT::JS(
      #   "function(thead) {",
      #   "  $(thead).css('font-size', '14px');",
      #   "}"
      #   )
  
```

## `r title` Dispositions Over Time By Division

-   **Select a time period to view total charge dispositions aggregated by week, month, quarter, or year.**
-   **Double click on a division/judge in the legend on the righthand side to display only their data.**
-   **Double click again to display all divisions.**

```{r}
#| echo: false
#| warning: false
#| message: false

library(plotly)
library(shiny)

# Create selectInput for time period
selectInput(inputId = "timePeriod",
            label = "Select time period:",
            choices = c("Week" = "week", "Month" = "month", "Quarter" = "quarter", "Year" = "year"),
            selected = "month")

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_charge_stats_1C_trial_week_.*csv$")
csv_dispo_list <- csv_dispo_list[-length(csv_dispo_list)]

charge_dispo_list <- lapply(paste0("WeeklyData/", csv_dispo_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
case_dispo_df <- bind_rows(setNames(charge_dispo_list, basename(csv_dispo_list)), .id = "id") #bind_rows(charge_dispo_list)

case_dispo_df2 <- case_dispo_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21", "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
         JRT = ACQJ + GLTJ,
         JWT = GLTW + ACQJ + AQRI,
         trials = JRT + JWT) %>% 
  group_by(Division, cyear) %>% 
  mutate(cumulative_dispo = cumsum(Total),
         cumulative_trials = cumsum(trials),
         cumulative_disposed = cumsum(Disposed),
         cumulative_awaiting = cumsum(Awaiting),
         cumulative_JRT = cumsum(JRT),
         cumulative_JWT = cumsum(JWT)) %>% 
  ungroup()

choicesCaseDispoSelect <- case_dispo_df2 %>% 
  select(Division) %>% 
  distinct() %>% 
  filter(Division != "All Divisions") %>% 
  arrange(Division) %>% 
  pull()

plotlyOutput("gg_dispos", height = 600)

# plotlyOutput("gg_dispo_divs_yearly", height = 600)
# plotlyOutput("gg_trial_divs_yearly", height = 600)
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(lubridate)
library(gghighlight)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_charge_stats_1C_trial_week_.*csv$")
csv_dispo_list <- csv_dispo_list[-length(csv_dispo_list)]

case_dispo_list <- lapply(paste0("WeeklyData/", csv_dispo_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
case_dispo_df <- bind_rows(setNames(case_dispo_list, basename(csv_dispo_list)), .id = "id") #bind_rows(case_dispo_list)

case_dispo_df1 <- case_dispo_df %>% 
    mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")), 
           cyear = format(trial_week, "%Y"),
           Division = if_else(Division == "-", "All Divisions", Division),
           Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21", "23", "All Divisions"), labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions"))
           )

aggregated_charge_data <- reactive({

  if(input$timePeriod == "week") {
    case_dispo_df1 %>%
      mutate(period = floor_date(trial_week, "week")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(Disposed), .groups = "drop") %>% 
      filter(Division != "All Divisions") # remove All Divisions, otherwise individual Division data is too compressed in plot
  } else if(input$timePeriod == "month") {
    case_dispo_df1 %>%
      mutate(period = floor_date(trial_week, "month")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(Disposed), .groups = "drop") %>% 
      filter(Division != "All Divisions") # remove All Divisions, otherwise individual Division data is too compressed in plot
  } else if(input$timePeriod == "quarter") {
    case_dispo_df1 %>%
      mutate(period = floor_date(trial_week, "quarter")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(Disposed), .groups = "drop") %>% 
      filter(Division != "All Divisions")
  } else if(input$timePeriod == "year") {
    case_dispo_df1 %>%
      mutate(period = floor_date(trial_week, "year")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(Disposed), .groups = "drop") %>% 
      filter(Division != "All Divisions") # remove All Divisions, otherwise individual Division data is too compressed in plot
    
  }
})

output$gg_dispos <- renderPlotly({
  case_dispo_divs <- aggregated_charge_data()
  
  if(input$timePeriod == "year") {
    case_dispo_divs <- case_dispo_divs %>%
      mutate(period_text = format(period, "%Y"))
  } else if(input$timePeriod == "quarter") {
    case_dispo_divs <- case_dispo_divs %>%
      mutate(period_text = paste0("Q", lubridate::quarter(period), " ", lubridate::year(period)))
  } else {
    case_dispo_divs <- case_dispo_divs %>%
      mutate(period_text = format(period, "%Y-%m-%d"))
  }
    
  # Set date range for rangeslider
  date_range_start <- min(case_dispo_divs$period)
  date_range_end <- max(case_dispo_divs$period)
  
# Set default plot start range based on time period
if(input$timePeriod == "week") {
  plot_start_range <- date_range_end - months(3) - days(7)  # Add 1 week padding
  plot_end_range <- date_range_end + days(7)  # Add 1 week padding
} else if(input$timePeriod == "month") {
  plot_start_range <- date_range_end - months(6) - days(15)  # Add ~2 weeks padding
  plot_end_range <- date_range_end + days(15)  # Add ~2 weeks padding
} else if(input$timePeriod == "quarter") {
  plot_start_range <- date_range_end - lubridate::years(2) - days(15)  # Add ~2 weeks padding
  plot_end_range <- date_range_end + days(15)  # Add ~2 weeks padding
} else {
  plot_start_range <- date_range_start - days(30)  # Add 1 month padding for year view
  plot_end_range <- date_range_end + days(30)  # Add 1 month padding
}
  
  # Determine tick settings based on time period
  if(input$timePeriod == "week") {
    tick_format <- "%b %d, %Y"
    dtick_val <- "M1"  # Monthly ticks for weekly data
  } else if(input$timePeriod == "month") {
    tick_format <- "%b %Y"
    dtick_val <- "M1"  # Quarterly ticks for monthly data
  } else if(input$timePeriod == "quarter") {
    tick_format <- "Q%q %Y"
    dtick_val <- "M3"  # Quarterly ticks
  } else {
    tick_format <- "%Y"
    dtick_val <- "M12"  # Yearly ticks for yearly data
  }

  gg_case_dispo_divs <- ggplot(case_dispo_divs,
                          aes(x = period, y = total_dispositions, group = Division, color = Division,
                              text = paste0("Period: ", period_text, "\n",
                                            "Division: ", Division, "\n",
                                            "Dispositions: ", total_dispositions)
                              )) +
    #gghighlight(Division == "1C01 (Wong)") +
    geom_line() +
    geom_point() +
    labs(x = paste(tools::toTitleCase(input$timePeriod), "Period"),
         y = "Total Dispositions",
         color = "Judge") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
    NULL
  
p_dispo <- ggplotly(gg_case_dispo_divs, tooltip = "text", dynamicTicks = TRUE) %>% 
    layout(
      xaxis = list(
        type = 'date',
        autorange = FALSE,
        tickmode = 'linear',
        tick0 = date_range_start,
        dtick = dtick_val,
        tickformat = tick_format,
        rangeselector = list(
          buttons = list(
            list(count = 3, label = "3m", step = "month", stepmode = "backward"),
            list(count = 6, label = "6m", step = "month", stepmode = "backward"),
            list(count = 1, label = "1y", step = "year", stepmode = "backward"),
            list(count = 2, label = "2y", step = "year", stepmode = "backward"),
            list(step = "all")
          )
        )
      )
    ) %>%
    rangeslider(type = 'date', start = plot_start_range, end = plot_end_range, thickness = 0.1) %>%
    config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

# Find trace indices by name (subtract 1 for zero-based indexing)
hide_names <- c("1C03 (Ho)", "1C13 (Viola)", "1C22 (Park)")
hide_indices <- which(sapply(p_dispo$x$data, function(trace) trace$name %in% hide_names))

p_dispo %>% 
  style(visible = "legendonly", traces = hide_indices)
  
  })


```

## Dispositions Trends By Division

```{r}
#| echo: false
#| warning: false
#| message: false

library(shiny)
library(ggplot2)
library(dplyr)
library(stringr)
library(plotly)

plotOutput("facet_divisions", height = 1200) 

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server
library(shiny)
library(ggplot2)
library(dplyr)
library(stringr)
library(plotly)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_charge_stats_1C_trial_week_.*csv$")
csv_dispo_list <- csv_dispo_list[-length(csv_dispo_list)]

  case_dispo_list <- lapply(paste0("WeeklyData/", csv_dispo_list), read.csv)
  # h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
  case_dispo_df <- bind_rows(setNames(case_dispo_list, basename(csv_dispo_list)), .id = "id") #bind_rows(case_dispo_list)
  
  case_dispo_division_df2 <- case_dispo_df %>% 
    mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
           cyear = format(trial_week, "%Y"),
           Division = if_else(Division == "-", "All Divisions", Division),
           Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                             labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
           JRT = ACQJ + GLTJ,
           JWT = GLTW + ACQJ + AQRI,
           trials = JRT + JWT) %>% 
    group_by(Division, cyear) %>% 
    mutate(cumulative_dispo = cumsum(Total),
           cumulative_trials = cumsum(trials),
           cumulative_JRT = cumsum(JRT),
           cumulative_JWT = cumsum(JWT)) %>% 
    ungroup()
  
  #df by month
    case_dispo_division_month <- case_dispo_division_df2 %>%
      mutate(period = floor_date(trial_week, "month")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(Disposed), .groups = "drop")
  
    #monthly facet graph
    # case_dispo_division_month %>% filter(Division != "All Divisions") %>% ggplot(aes(x = period, y = total_dispositions, group = Division, color = Division)) + 
    # geom_col(aes(fill = Division)) + 
    # facet_wrap(vars(class = Division)) +
    # labs(x = NULL) +
    # theme_bw() +
    # theme(strip.text.x = element_text(size = 25, face = "bold"), 
    #       legend.position="none",
    #       axis.text.x.bottom = element_text(size = 18),
    #       axis.text.y.left = element_text(size = 18),
    #       axis.title.y = element_text(size = 25, face = "bold")
    #       ) + 
    #   scale_x_date(breaks = "1 month", date_labels = "%b")
    
  output$facet_divisions <- renderPlot({
  case_dispo_division_df2 %>% filter(Division != "All Divisions") %>% ggplot(aes(x = trial_week, y = Disposed, group = Division, color = Division)) + 
    geom_col(aes(fill = Division)) + 
    facet_wrap(vars(class = Division)) +
    labs(x = NULL) +
    theme_bw() +
    theme(strip.text.x = element_text(size = 25, face = "bold"), 
          legend.position="none",
          axis.text.x.bottom = element_text(size = 18),
          axis.text.y.left = element_text(size = 18),
          axis.title.y = element_text(size = 25, face = "bold")
          ) + 
      scale_x_date(breaks = "1 month", date_labels = "%b")
    } 
  ) 
```

## `r title` Disposition Trends in First Circuit in Aggregate

This graph shows the number of dispositions across all divisions over time. The blue lines show the cumulative counts and the black lines show the weekly counts.

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-height: 6

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(gghighlight)
library(tidyr)
library(ggtext)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_charge_stats_1C_trial_week_.*csv$")
csv_dispo_list <- csv_dispo_list[-length(csv_dispo_list)]

case_dispo_list <- lapply(paste0("WeeklyData/", csv_dispo_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_dispo_df <- bind_rows(setNames(case_dispo_list, basename(csv_dispo_list)), .id = "id") #bind_rows(case_dispo_list)

charge_dispo_aggregate_df <- charge_dispo_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
         JRT = ACQJ + GLTJ,
         JWT = GLTW + ACQJ + AQRI,
         trials = JRT + JWT) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Total Dispositions` = cumsum(Total),
         `Total Disposed` = cumsum(Disposed), 
         `Total Awaiting` = cumsum(Awaiting),
         #cumulative_trials = cumsum(trials),
         #cumulative_JRT = cumsum(JRT),
         #cumulative_JWT = cumsum(JWT)
         ) %>% 
  rename(`Weekly Disposed` = Disposed) %>% 
  ungroup()

charge_dispo_aggregate_df_long <- charge_dispo_aggregate_df %>% 
  pivot_longer(
    cols = c(`Weekly Disposed`, `Total Dispositions`:`Total Awaiting`), 
    names_to = "Type", 
    values_to = "Dispositions")

charge_dispo_aggregate_df_long$Type <- factor(charge_dispo_aggregate_df_long$Type, levels = c("Total Dispositions", "Total Disposed", "Total Awaiting", "Weekly Disposed"))

cumulative_dispositions_aggregate_line <- subset(charge_dispo_aggregate_df_long, Type != "Weekly Disposed") %>% filter(Division == "All Divisions")
weekly_dispositions_aggregate_bar <- subset(charge_dispo_aggregate_df_long, Type == "Weekly Disposed") %>% filter(Division == "All Divisions")

#Graph 2: Weekly and Cumulative Dispos
gg_dispo_all <- ggplot(cumulative_dispositions_aggregate_line %>% filter(Division == "All Divisions"),
                       aes(x = trial_week, y = Dispositions, group = Type, colour = Type,
                           text = paste0("week: ",trial_week,"\n",
                                         "Weekly Dispositions: ", Total, "\n",
                                         "cumulative # of dispositions:",
                                         Dispositions, "\n",
                                         "division: ", Division, "\n",
                                         "year: ", cyear))) +
geom_col(data = weekly_dispositions_aggregate_bar,fill = "#FFFFFF", aes(x = trial_week, y = Dispositions, group = Type,                             text = paste0("week: ",trial_week,"\n",
                                         "Weekly Dispositions: ", Total, "\n",
                                         "division: ", Division, "\n",
                                         "year: ", cyear))) +
  scale_color_manual(values=c("#000000", "#0000FF", "#00FF00", "#FF0000")) +
  geom_point() +
  geom_line() +
    #ISSUE: the x-axis was showing an extra label on each end of plot, tried a few methods to fix this:
  # scale_x_date("Week", date_breaks = "1 week") +
  # scale_x_date(date_breaks = "1 week", date_labels = "%m-%d-%y") +
  scale_x_date(breaks = seq(as.Date("2024-01-01"), max(charge_dispo_aggregate_df$trial_week), by = 7), date_labels = "%m-%d-%y") +
  scale_y_continuous(limits = c(0,NA)) +
  # scale_y_continuous("Total Pending Trials") +
  # scale_color_discrete("Divisions") +
  labs(title = "Weekly and Cumulative Dispos (All Divisions)",
       x = "Date",
       y = "Number of dispositions",
       color = NULL) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 30)) #+
#NULL

ggplotly(gg_dispo_all, tooltip = "text", dynamicTicks = TRUE) %>%
      # hide_legend() %>%
      layout(
        #moved title and subtitle to the shinydashboard box b/c it didn't format nicely with selectorbuttons, especially on smaller screens
        title = list(text=paste0('Weekly and Cumulative Dispos (All Divisions)')
                     # xanchor = 'left', #reposition title
                     # yanchor =  'top'  #reposition title
                     ),
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     # range = as.Date(c(plotStartRange,plotEndRange)),
                     rangeselector = list(
                       buttons = list(
                          list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )
                     ),
                     tickmode = 'linear',  
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y')             
                     ) %>%
      # rangeslider(type = 'date', start = min(case_dispo_df2$trial_week) - 7, end = max(case_dispo_df2$trial_week) + 7, thickness = .1) %>% # use +/- 7 to add some padding to left and right side of plot and rangeslider
  rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

```

## `r title` Disposition Trends in First Circuit by Division

This graph shows the number of divisions by each division. Use the dropdown to select a specific division.

```{r}
#| echo: false
#| warning: false
#| message: false

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(gghighlight)
library(ggtext)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_charge_stats_1C_trial_week_.*csv$")
csv_dispo_list <- csv_dispo_list[-length(csv_dispo_list)]

charge_dispo_list <- lapply(paste0("WeeklyData/", csv_dispo_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_dispo_df <- bind_rows(setNames(charge_dispo_list, basename(csv_dispo_list)), .id = "id") #bind_rows(case_dispo_list)

charge_dispo_division <- charge_dispo_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)",  "1C23 (Somerville)", "All Divisions")),
         JRT = ACQJ + GLTJ,
         JWT = GLTW + ACQJ + AQRI,
         trials = JRT + JWT) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Weekly Disposed` = Disposed,
         `Total Dispositions` = cumsum(Total),
         `Total Disposed` = cumsum(Disposed),
         `Total Awaiting` = cumsum(Awaiting),
         cumulative_JRT = cumsum(JRT),
         cumulative_JWT = cumsum(JWT),
         cumulative_trials = cumsum(trials)) %>%   
  ungroup()

charge_dispo_division_long <- charge_dispo_division %>% pivot_longer(cols = c(`Weekly Disposed`, `Total Dispositions`:`Total Awaiting`), values_to = "Dispositions")

choicesCaseDispoSelect <- charge_dispo_division_long %>% 
  select(Division) %>% 
  distinct() %>% 
  filter(Division != "All Divisions") %>% 
  arrange(Division) %>% 
  pull()

selectizeInput(inputId = "caseDispoSelect",
               label = "Select Division:",
               choices = choicesCaseDispoSelect,
               selected = choicesCaseDispoSelect[1],
               multiple = FALSE
               )

plotlyOutput("gg_dispo_divs", height = 600)

#plotlyOutput("gg_trial_divs", height = 600)

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(tidyr)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_stats_1C_trial_week_ to dispo_case_stats_1C_trial_week_)
csv_dispo_list <- list.files("WeeklyData/", pattern = "^dispo_charge_stats_1C_trial_week_.*csv$")
csv_dispo_list <- csv_dispo_list[-length(csv_dispo_list)]

charge_dispo_list <- lapply(paste0("WeeklyData/", csv_dispo_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_dispo_df <- bind_rows(setNames(charge_dispo_list, basename(csv_dispo_list)), .id = "id") #bind_rows(case_dispo_list)

charge_dispo_division <- charge_dispo_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)",  "1C23 (Somerville)", "All Divisions")),
         JRT = ACQJ + GLTJ,
         JWT = GLTW + ACQJ + AQRI,
         trials = JRT + JWT) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Weekly Disposed` = Disposed,
         `Total Dispositions` = cumsum(Total),
         `Total Disposed` = cumsum(Disposed),
         `Total Awaiting` = cumsum(Awaiting)) %>%
         #cumulative_JRT = cumsum(JRT),
         #cumulative_JWT = cumsum(JWT))  
  ungroup()

charge_dispo_division_long <- charge_dispo_division %>% pivot_longer(cols = c(`Weekly Disposed`, `Total Dispositions`:`Total Awaiting`), values_to = "Dispositions", names_to = "Type")

charge_dispo_division_long$Type <- factor(charge_dispo_division_long$Type, levels = c("Total Dispositions", "Total Disposed", "Total Awaiting", "Weekly Disposed"))

charge_dispo_division_line <- subset(charge_dispo_division_long, Type != "Weekly Disposed") %>% filter(Division != "All Divisions")
charge_dispo_division_bar <- subset(charge_dispo_division_long, Type == "Weekly Disposed") %>% filter(Division != "All Divisions")

  charge_dispo_df2 <- reactive({charge_dispo_division_line %>% 
    group_by(Division, cyear) %>% 
    mutate(cumulative_dispo = cumsum(Total),
           cumulative_trials = cumsum(trials)) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})

    charge_dispo_bar <- reactive({charge_dispo_division_bar %>% 
    group_by(Division, cyear) %>% 
    mutate(cumulative_dispo = cumsum(Total),
           cumulative_trials = cumsum(trials)) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})
  
yaxis_lims <- charge_dispo_df %>% 
    mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
           Division = if_else(Division == "-", "All Divisions", Division),
           Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                             labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
         JRT = ACQJ + GLTJ,
         JWT = GLTW + ACQJ + AQRI,
         trials = JRT + JWT) %>% 
    filter(Division != "All Divisions") %>%
    group_by(Judge) %>% 
    summarize(total_dispos = sum(Total),
           total_trials = sum(trials)) %>% 
    ungroup() %>%
  filter(Judge != "Total")

ymax_dispos <- max(yaxis_lims$total_dispos) + 1
ymax_trials <- max(yaxis_lims$total_trials) + 1
  
output$gg_dispo_divs <- renderPlotly({
  
  gg_dispo_divs <- ggplot(charge_dispo_df2(),
                          aes(x = trial_week, y = Dispositions, group = Type, colour = Type,
                              text = paste0("week: ",trial_week,"\n",
                                             "Weekly dispositions: ", Total, "\n",
                                            "cumulative # of dispositions:", Dispositions, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
    geom_col(charge_dispo_bar(), 
             fill = "#FFFFFF", 
             mapping = aes(x = trial_week, y = Dispositions, group = Type, 
                           text = paste0("week: ",trial_week,"\n",
                                             "Weekly dispositions: ", Total, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
    geom_point() +
    geom_line() +
  scale_color_manual(values=c("#000000", "#0000FF", "#00FF00", "#FF0000")) +
    scale_x_date(breaks = seq(as.Date("2024-01-01"), max(charge_dispo_df2()$trial_week), by = 7), date_labels = "%m-%d-%y") +
    scale_y_continuous(limits = c(0, ymax_dispos)) +
    labs(title = paste0("Weekly and Cumulative Dispos in ", input$caseDispoSelect),
         x = NULL,
         y = "Number of dispositions",
         color = "Divisions") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 30)) + 
    NULL
  
ggplotly(gg_dispo_divs,tooltip = "text", dynamicTicks = TRUE) %>%
      # hide_legend() %>%
      layout(
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     # range = as.Date(c(plotStartRange,plotEndRange)),
                     rangeselector = list(
                       buttons = list(
                         list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )
                     ),
                     tickmode = 'linear', 
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y' #added this b/c tick labels formatted with ggplot were being cutoff by graph, this allows correct alignment and spacing
                     ),   
        #to customize both range and # of tick labels, use this instead of the above
        #https://plotly.com/r/time-series/
        #h/t: https://stackoverflow.com/questions/71823559/how-to-set-custom-date-ticks-breaks-in-plotly
                  yaxis = list(autorange = FALSE)
             ) %>%
      rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

})


```

# Trials (`r title` Level)

## Weekly Trial Table

The table below shows the number of trials across each criminal division in the First Circuit, Circuit Court. Use the drop down to look at historical weekly reports.

```{r}
#| echo: false
#| warning: false
#| message: false
library(dplyr)
library(stringr)
library(shiny)
library(htmltools)
library(DT)

csv_trial_list <- list.files("WeeklyData/", pattern = "^dispo_charge_trial_stats_1C_trial_week_.*csv$")
run_dates_trial <- str_extract(csv_trial_list, "[0-9]{4}-[0-9]{2}-[0-9]{2}")
run_dates_aggregate <- str_extract(csv_trial_list, "Aggregate")
run_dates_trial <- append(run_dates_trial,run_dates_aggregate)
run_dates_trial <- run_dates_trial[!is.na(run_dates_trial)]
# pending_trial_list <- lapply(paste0("../pending_trials/", csv_list), read.csv)

selectizeInput(inputId = "selectWeekDispo_Trial",
               label = "Select a report:",
               choices = rev(run_dates_trial),
               selected = TRUE)

tableOutput("trial_table")

#attempt to add download button using just shiny widgets to save table displayed with Kable
# downloadButton(outputId = "saveCSV", label = "CSV")

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(kableExtra)
library(DT)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_trial_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)
weekly_trial_table <- reactive({
    csv_selected <- list.files("WeeklyData/", pattern = paste0("^dispo_charge_trial_stats_1C_trial_week_", input$selectWeekDispo_Trial,".*?csv$"))
  dispo_trial_table_full <- read.csv(file = paste0("WeeklyData/", csv_selected))
  
  })

  output$trial_table <- function(){
      weekly_trial_table() %>% 
      rename(`Jury Trials` = JuryTrials, 
             `Bench Trials` = BenchTrials) %>% 
    kable() %>% 
      kable_styling("striped","hover", font_size = 14)
    }

# output$trial_table <- renderDT(
#   weekly_trial_table(), 
#   rownames = F,
#   # colnames = c("Trial week", "1C01 (Wong)", "1C02 (Remigio)", "1C11 (Souza)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C23 (Somerville)", "Total"),
#     # colnames = c("Judge\n","Division","JRT","JWT","COP","DSM","DWO","DPJ","NPQ","RMD","MISC","Total"),
#     extensions = c("Buttons", "FixedColumns"),
#     options = list(
#       pageLength = 15,
#       # lengthMenu = c(15, 25, 50),
#       # scrollY = "600px", #this was creating some weird behavior in which the column heads of previous table were partially appearing
#       scrollX = TRUE,
#       #add buttons, and specifying dom
#       #https://stackoverflow.com/questions/50039186/add-download-buttons-in-dtrenderdatatable
#       #https://stackoverflow.com/questions/50043152/r-shiny-how-to-add-pagination-in-dtrenderdatatable
#       # dom = 'Bfrtip',
#       dom = 'tB',
#       buttons = c('copy','csv','excel','pdf'),
#       fixedColumns = list(leftColumns = 1)  # Freeze first column
#       # h/t: customize font size of column heads: https://github.com/rstudio/DT/issues/783
#       # headerCallback = DT::JS(
#       #   "function(thead) {",
#       #   "  $(thead).css('font-size', '14px');",
#       #   "}"
#       #   )
#     )
# )

```

## Trial Trends By Division

```{r}
#| echo: false
#| warning: false
#| message: false

library(shiny)
library(ggplot2)
library(dplyr)
library(stringr)
library(plotly)

plotOutput("facet_trials", height = 1200) 

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_trial_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)
csv_trial_list <- list.files("WeeklyData/", pattern = "^dispo_charge_trial_stats_1C_trial_week_.*csv$")
csv_trial_list <- csv_trial_list[-length(csv_trial_list)]

case_trial_list <- lapply(paste0("WeeklyData/", csv_trial_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
case_trial_df <- bind_rows(setNames(case_trial_list, basename(csv_trial_list)), .id = "id") #bind_rows(case_dispo_list)

case_trial_division_df <- case_trial_df %>% 
  rename(`Jury Trials` = JuryTrials,
         `Bench Trials` = BenchTrials) %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)",  "1C23 (Somerville)", "All Divisions")),
         `Weekly Trials` = `Jury Trials` + `Bench Trials`) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Total Trials` = cumsum(`Weekly Trials`),
         `Jury Trials` = cumsum(`Jury Trials`),
         `Bench Trials` = cumsum(`Bench Trials`)) %>% 
  ungroup()
  
  #try by month
    case_trial_division_month <- case_trial_division_df %>%
      mutate(period = floor_date(trial_week, "month")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(`Weekly Trials`), .groups = "drop")
  
    case_trial_division_month %>% filter(Division != "All Divisions") %>% ggplot(aes(x = period, y = total_dispositions, group = Division, color = Division)) + 
    geom_col(aes(fill = Division)) + 
    facet_wrap(vars(class = Division)) +
    labs(x = NULL) +
    theme_bw() +
    theme(strip.text.x = element_text(size = 25, face = "bold"), 
          legend.position="none",
          axis.text.x.bottom = element_text(size = 18),
          axis.text.y.left = element_text(size = 18),
          axis.title.y = element_text(size = 25, face = "bold")
          ) + 
      scale_x_date(breaks = "1 month", date_labels = "%b")

  output$facet_trials <- renderPlot({
  case_trial_division_df %>% filter(Division != "All Divisions") %>% ggplot(aes(x = trial_week, y = Total, group = Division, color = Division)) + 
    geom_col(aes(fill = Division)) + 
    facet_wrap(vars(class = Division)) +
    labs(x = NULL) +
    theme_bw() +   
    theme(strip.text.x = element_text(size = 25, face = "bold"), 
          legend.position="none",
          axis.text.x.bottom = element_text(size = 18),
          axis.text.y.left = element_text(size = 18),
          axis.title.y = element_text(size = 25, face = "bold")
          )  
      } 
  ) 
```

## Weekly and Cumulative Trials

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig-height: 6

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(gghighlight)
library(tidyr)
library(ggtext)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_trial_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)
csv_trial_list <- list.files("WeeklyData/", pattern = "^dispo_charge_trial_stats_1C_trial_week_.*csv$")
csv_trial_list <- csv_trial_list[-length(csv_trial_list)]

charge_trial_list <- lapply(paste0("WeeklyData/", csv_trial_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_trial_df <- bind_rows(setNames(charge_trial_list, basename(csv_trial_list)), .id = "id") #bind_rows(case_dispo_list)

case_trial_aggregate_df <- charge_trial_df %>% 
  rename(`Jury Trials` = JuryTrials,
         `Bench Trials` = BenchTrials) %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21", "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)",  "1C23 (Somerville)", "All Divisions")),
         `Weekly Trials` = `Jury Trials` + `Bench Trials`) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Total Trials` = cumsum(`Weekly Trials`),
         `Jury Trials` = cumsum(`Jury Trials`),
         `Bench Trials` = cumsum(`Bench Trials`)) %>% 
  ungroup()

#Cumulative Trial Graph
case_trial_aggregate_long <- case_trial_aggregate_df %>% pivot_longer(cols = c("Jury Trials", "Bench Trials", "Weekly Trials", "Total Trials"), names_to = "Type", values_to = "Trials") 
case_trial_aggregate_long$Type <- factor(case_trial_aggregate_long$Type, levels = c("Total Trials", "Jury Trials", "Bench Trials", "Weekly Trials"))

cumulative_trials_aggregate_line <- subset(case_trial_aggregate_long, Type != "Weekly Trials") %>% filter(Division == "All Divisions")
weekly_trials_aggregate_bar <- subset(case_trial_aggregate_long, Type == "Weekly Trials") %>% filter(Division == "All Divisions")

gg_trial <- ggplot(cumulative_trials_aggregate_line %>% filter(Division == "All Divisions"), 
                   aes(x = trial_week, y = Trials, group = Type, colour = Type,
                    text = paste0("week: ",trial_week,"\n",
                    "# of trials: ", Trials, "\n",
                    "division: ", Division, "\n",
                    "year: ", cyear))) +
   geom_col(data = weekly_trials_aggregate_bar,fill = "#FFFFFF", aes(x = trial_week, y = Trials, group =  Type)) +
  scale_color_manual(values=c("#000000", "#0000FF", "#00FF00", "#FF0000")) +
  geom_point() +
  geom_line() +
 
  scale_x_date(breaks = seq(as.Date("2024-01-01"), max(case_trial_aggregate_df$trial_week), by = 7), date_labels = "%m-%d-%y") +
  scale_y_continuous(limits = c(0,NA)) +
  labs(title = "Weekly and Cumulative Trials (All Divisions)",
       x = NULL,
       y = "Number of trials",
       color = "Trial Type") +
  theme_bw() +
  theme(plot.subtitle = element_markdown(size = 11)) +
  theme(axis.text.x = element_text(angle = 30)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(legend.text = element_text(size = 11)) +
  NULL 
  
ggplotly(gg_trial, tooltip = "text", dynamicTicks = TRUE) %>%
      layout(
        title = list(text=paste0('Weekly and Cumulative Trials (All Divisions)')
                     ),
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     rangeselector = list(
                       buttons = list(
                         list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )#,
                       # x = 0.6,           #put rangeselector on right side
                       # xanchor = "left"   #put rangeselector on right side
                     ),
                    
                     tickmode = 'linear', 
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y' 
                     )
             ) %>%
       rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

```

## Weekly and Cumulative Trials By Division

```{r}
#| echo: false
#| warning: false
#| message: false

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(gghighlight)
library(ggtext)

choicesCaseDispoSelect <- case_dispo_df2 %>% 
  select(Division) %>% 
  distinct() %>% 
  filter(Division != "All Divisions") %>% 
  arrange(Division) %>% 
  pull()

# selectizeInput(inputId = "caseDispoSelect",
#                label = "Select Division:",
#                choices = choicesCaseDispoSelect,
#                selected = choicesCaseDispoSelect[1],
#                multiple = TRUE
#                )

selectizeInput(inputId = "caseDispoSelect",
               label = "Select Division:",
               choices = choicesCaseDispoSelect,
               selected = choicesCaseDispoSelect[1],
               multiple = FALSE
               )

plotlyOutput("gg_trial_divs", height = 600)

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(tidyr)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_trial_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)
csv_trial_list <- list.files("WeeklyData/", pattern = "^dispo_charge_trial_stats_1C_trial_week_.*csv$")
csv_trial_list <- csv_trial_list[-length(csv_trial_list)]

charge_trial_list <- lapply(paste0("WeeklyData/", csv_trial_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_trial_df <- bind_rows(setNames(charge_trial_list, basename(csv_trial_list)), .id = "id") #bind_rows(case_dispo_list)

charge_trials_division <- charge_trial_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)",  "1C23 (Somerville)", "All Divisions"))
         ) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Weekly Trials` = Total,
         `Total Jury Trials` = cumsum(JuryTrials),
         `Total Bench Trials` = cumsum(BenchTrials),
         `Total Trials` = cumsum(Total)) %>%   
  ungroup()

charge_trials_division_long <- charge_trials_division %>% pivot_longer(cols = c(`Weekly Trials`, `Total Jury Trials`:`Total Trials`), values_to = "Trials", names_to = "Type") 

charge_trials_division_long$Type <- factor(charge_trials_division_long$Type, levels = c("Total Trials", "Total Jury Trials", "Total Bench Trials", "Weekly Trials"))

charge_trials_division_line <- subset(charge_trials_division_long, Type != "Weekly Trials") %>% filter(Division != "All Divisions")
charge_trials_division_bar <- subset(charge_trials_division_long, Type == "Weekly Trials") %>% filter(Division != "All Divisions")

  charge_trials_df2 <- reactive({charge_trials_division_line %>% 
    group_by(Division, cyear) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})

    charge_trials_bar <- reactive({charge_trials_division_bar %>% 
    group_by(Division, cyear) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})

output$gg_trial_divs <- renderPlotly({
  
  gg_trial_divs <- ggplot(charge_trials_df2(),
                          aes(x = trial_week, y = Trials, group = Type, colour = Type,
                              text = paste0("week: ",trial_week,"\n",
                                            "cumulative # of trials:", Trials, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
    geom_col(charge_trials_bar(), 
             fill = "#FFFFFF", 
             mapping = aes(x = trial_week, y = Trials, group = Type, 
                           text = paste0("week: ",trial_week,"\n",
                                             "Weekly Trials: ", Trials, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
    geom_point() +
    geom_line() +
  scale_color_manual(values=c("#000000", "#0000FF", "#00FF00", "#FF0000")) +
    geom_point() +
    geom_line() +
    #ISSUE: the x-axis was showing an extra label on each end of plot, tried a few methods to fix this
    # scale_x_date("Week", date_breaks = "1 week") +
    # scale_x_date(date_breaks = "1 week", date_labels = "%m-%d-%y") +
    scale_x_date(breaks = seq(as.Date("2024-01-01"), max(charge_trials_df2()$trial_week), by = 7), date_labels = "%m-%d-%y") +
    #ISSUE: for judges with 0 or few trials, the y-axis has non-integer values, looks bad, use method 1 as a fix:
    #method 0:
    # scale_y_continuous(limits = c(0,NA)) +
    #method 1:
    scale_y_continuous(limits = c(0, ymax_trials)) +
    #method 2:
    # scale_y_continuous(breaks = seq(0, sum(case_dispo_df2()$Total) + 1, by = 5)) +
    # scale_y_continuous("Total Pending Trials") +
    # scale_color_discrete("Divisions") +
    labs(title = paste0("Weekly and Cumulative Trials in ", input$caseDispoSelect),
         x = NULL,
         y = "Number of trials",
         color = "Divisions") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 30)) +
         NULL

ggplotly(gg_trial_divs,tooltip = "text", dynamicTicks = TRUE) %>%
      # hide_legend() %>%
      layout(
        #moved title and subtitle to the shinydashboard box b/c it didn't format nicely with selectorbuttons, especially on smaller screens
        # title = list(text=paste0('Weekly and Cumulative Trials (All Divisions)')
        #              # xanchor = 'left', #reposition title
        #              # yanchor =  'top'  #reposition title
        #              ),
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     # range = as.Date(c(plotStartRange,plotEndRange)),
                     rangeselector = list(
                       buttons = list(
                         list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )#,
                       # x = 0.6,           #put rangeselector on right side
                       # xanchor = "left"   #put rangeselector on right side
                     ),
                     #for dates on x-axis, this worked: tickmode = linear and set both tick0/dtick
                     #for % on y-axis, this worked: tickmode = array and set both tickvals/ticktext
                     #h/t: https://stackoverflow.com/questions/68475195/dticks-and-plotly-how-to-control-what-is-shown-on-x-axes
                     tickmode = 'linear', 
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y' #added this b/c tick labels formatted with ggplot were being cutoff by graph, this allows correct alignment and spacing
                     ),   
        #to customize both range and # of tick labels, use this instead of the above
        #https://plotly.com/r/time-series/
        #h/t: https://stackoverflow.com/questions/71823559/how-to-set-custom-date-ticks-breaks-in-plotly
        # yaxis = list(range = c(-0.05,1.05), #changed from 0,1 to -.05,1.05 to add small margin/padding at ends of graph
        #              autorange = FALSE,
        #              tickmode = 'array',
        #              tickvals = seq(0,1,.1),
        #              ticktext = paste0(seq(0,100,10),'%'))
          yaxis = list(autorange = FALSE)
             ) %>%

      # rangeslider(type = 'date', start = min(case_dispo_df2()$trial_week) - 7, end = max(case_dispo_df2()$trial_week) + 7, thickness = .1) %>% # use +/- 7 to add some padding to left and right side of plot and rangeslider
      rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

})
```

# Deferrals (`r title` Level)

## Weekly Deferral Table

The table below shows the number of deferrals and their outcomes (successful, unsuccessful) across each criminal division in the First Circuit, Circuit Court. Use the drop down to look at historical weekly reports.

```{r}
#| echo: false
#| warning: false
#| message: false
library(dplyr)
library(stringr)
library(shiny)
library(htmltools)
library(DT)
library(ggtext)

csv_deferral_list <- list.files("WeeklyData/", pattern = "^dispo_charge_deferral_stats_1C_trial_week_.*csv$")
run_dates_deferral <- str_extract(csv_deferral_list, "[0-9]{4}-[0-9]{2}-[0-9]{2}")
run_dates_aggregate <- str_extract(csv_deferral_list, "Aggregate")
run_dates_deferral <- append(run_dates_deferral,run_dates_aggregate)
run_dates_deferral <- run_dates_deferral[!is.na(run_dates_deferral)]

selectizeInput(inputId = "selectWeekDispo_Deferral",
               label = "Select a report:",
               choices = rev(run_dates_deferral),
               selected = TRUE)
  
DTOutput("deferral_table")

#attempt to add download button using just shiny widgets to save table displayed with Kable
# downloadButton(outputId = "saveCSV", label = "CSV")

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(kableExtra)
library(DT)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_deferral_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)

weekly_deferral_table <- reactive({
    csv_selected <- list.files("WeeklyData/", pattern = paste0("^dispo_charge_deferral_stats_1C_trial_week_", input$selectWeekDispo_Deferral,".*?csv$"))
  dispo_trial_table_full <- read.csv(file = paste0("WeeklyData/", csv_selected))
  })

output$deferral_table <- renderDT(
  weekly_deferral_table(), 
  rownames = F,
  # colnames = c("Trial week", "1C01 (Wong)", "1C02 (Remigio)", "1C03 (Ho)", "1C11 (Souza)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C22 (Park)", "1C23 (Somerville)", "Total"),
    # colnames = c("Judge\n","Division","JRT","JWT","COP","DSM","DWO","DPJ","NPQ","RMD","MISC","Total"),
    extensions = c("Buttons", "FixedColumns"),
    options = list(
      pageLength = 15,
      # lengthMenu = c(15, 25, 50),
      # scrollY = "600px", #this was creating some weird behavior in which the column heads of previous table were partially appearing
      scrollX = TRUE,
      #add buttons, and specifying dom
      #https://stackoverflow.com/questions/50039186/add-download-buttons-in-dtrenderdatatable
      #https://stackoverflow.com/questions/50043152/r-shiny-how-to-add-pagination-in-dtrenderdatatable
      # dom = 'Bfrtip',
      dom = 'tB',
      buttons = c('copy','csv','excel','pdf'),
      fixedColumns = list(leftColumns = 1)  # Freeze first column
      # h/t: customize font size of column heads: https://github.com/rstudio/DT/issues/783
      # headerCallback = DT::JS(
      #   "function(thead) {",
      #   "  $(thead).css('font-size', '14px');",
      #   "}"
      #   )
    )
)

```

## Deferral Trends By Division

```{r}
#| echo: false
#| warning: false
#| message: false

library(shiny)
library(ggplot2)
library(dplyr)
library(stringr)
library(plotly)

plotOutput("facet_deferrals", height = 1200) 

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_deferral_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)
csv_deferral_list <- list.files("WeeklyData/", pattern = "^dispo_charge_deferral_stats_1C_trial_week_.*csv$")
csv_deferral_list <- csv_deferral_list[-length(csv_deferral_list)]

case_deferral_list <- lapply(paste0("WeeklyData/", csv_deferral_list), read.csv)

case_deferral_df <- bind_rows(setNames(case_deferral_list, basename(csv_deferral_list)), .id = "id") #bind_rows(case_dispo_list)
  
  case_deferral_division <- case_deferral_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
  `Weekly Deferrals` = Successful + Unsuccessful) %>% 
  group_by(Division, cyear) %>% 
  mutate(
         `Total Deferrals` = cumsum(Total),
         `Successful Deferrals` = cumsum(Successful),
         `Unsuccessful Deferrals` = cumsum(Unsuccessful)) %>% 
  ungroup()
  
  #df by month
    case_deferral_division_month <- case_deferral_division %>%
      mutate(period = floor_date(trial_week, "month")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(`Weekly Deferrals`), .groups = "drop")
  
    #monthly facet graph
     # case_deferral_division_month %>% filter(Division != "All Divisions") %>% ggplot(aes(x = period, y = total_dispositions, group = Division, color = Division)) + 
     # geom_col(aes(fill = Division)) + 
     # facet_wrap(vars(class = Division)) +
     # labs(x = NULL) +
     # theme_bw() +
     # theme(strip.text.x = element_text(size = 25, face = "bold"), 
     #       legend.position="none",
     #       axis.text.x.bottom = element_text(size = 18),
     #       axis.text.y.left = element_text(size = 18),
     #       axis.title.y = element_text(size = 25, face = "bold")
     #       ) + 
     #   scale_x_date(breaks = "1 month", date_labels = "%b")
     
  output$facet_deferrals <- renderPlot({
  
    case_deferral_division %>% filter(Division != "All Divisions") %>% ggplot(aes(x = trial_week, y = Total, group = Division, color = Division)) + 
    geom_col(aes(fill = Division)) + 
    facet_wrap(vars(class = Division)) +
    labs(x = NULL) +
    theme_bw() +
    theme(strip.text.x = element_text(size = 25, face = "bold"), 
          legend.position="none",
          axis.text.x.bottom = element_text(size = 18),
          axis.text.y.left = element_text(size = 18),
          axis.title.y = element_text(size = 25, face = "bold")
          ) 
    } 
  ) 
```

## Weekly and Cumulative Deferrals

```{r}
#| echo: false
#| warning: false
#| message: false

library(dplyr)
library(ggplot2)
library(stringr)
library(tidyr)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_deferral_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)
csv_deferral_list <- list.files("WeeklyData/", pattern = "^dispo_charge_deferral_stats_1C_trial_week_.*csv$")
csv_deferral_list <- csv_deferral_list[-length(csv_deferral_list)]

charge_deferral_list <- lapply(paste0("WeeklyData/", csv_deferral_list), read.csv)
charge_deferral_df <- bind_rows(setNames(charge_deferral_list, basename(csv_deferral_list)), .id = "id") #bind_rows(case_dispo_list)

charge_deferral_aggregate <- charge_deferral_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2",  "6", "11", "13", "15", "17", "19", "20", "21", "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
  `Weekly Deferrals` = Successful + Unsuccessful) %>% 
  group_by(Division, cyear) %>% 
  mutate(
         `Total Deferrals` = cumsum(Total),
         `Successful Deferrals` = cumsum(Successful),
         `Unsuccessful Deferrals` = cumsum(Unsuccessful)) %>% 
  ungroup()

charge_deferral_aggregate_long <- charge_deferral_aggregate %>% pivot_longer(cols = c(`Weekly Deferrals`:`Unsuccessful Deferrals`), names_to = "Type", values_to = "Deferrals")

charge_deferral_aggregate_long$Type <- factor(charge_deferral_aggregate_long$Type, levels = c("Total Deferrals", "Successful Deferrals", "Unsuccessful Deferrals", "Weekly Deferrals"))

cumulative_deferrals_aggregate_line <- subset(charge_deferral_aggregate_long, Type != "Weekly Deferrals") %>% filter(Division == "All Divisions")
weekly_deferrals_aggregate_bar <- subset(charge_deferral_aggregate_long, Type == "Weekly Deferrals") %>% filter(Division == "All Divisions")

gg_deferral_all <- ggplot(cumulative_deferrals_aggregate_line %>% filter(Division == "All Divisions"),
                          aes(x = trial_week, y = Deferrals, colour = Type, group = Type,
                              text = paste0("week: ",trial_week,"\n",
                                            "# of dispositions: ", Deferrals, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
   geom_col(data = weekly_deferrals_aggregate_bar,fill = "#FFFFFF", aes(x = trial_week, y = Deferrals, group =  Type)) +
  geom_point() +
  geom_line() +
   scale_color_manual(values=c("#000000", "#0000FF", "#00FF00", "#FF0000")) + 
  #ISSUE: the x-axis was showing an extra label on each end of plot, tried a few methods to fix this:
  # scale_x_date("Week", date_breaks = "1 week") +
  # scale_x_date(date_breaks = "1 week", date_labels = "%m-%d-%y") +
  scale_x_date(breaks = seq(as.Date("2024-01-01"), max(charge_deferral_aggregate$trial_week), by = 7), date_labels = "%m-%d-%y") +
  scale_y_continuous(limits = c(0,NA)) +
  # scale_y_continuous("Total Pending Trials") +
  # scale_color_discrete("Divisions") +
  labs(title = "Weekly and Cumulative Deferrals and Outcomes (All Divisions)",
       x = NULL,
       y = "Number of dispositions",
       color = NULL) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 30)) +
  NULL

ggplotly(gg_deferral_all, tooltip = "text", dynamicTicks = TRUE) %>%
      # hide_legend() %>%
      layout(
        #moved title and subtitle to the shinydashboard box b/c it didn't format nicely with selectorbuttons, especially on smaller screens
        title = list(text=paste0('Weekly and Cumulative Dispos (All Divisions)')
                     # xanchor = 'left', #reposition title
                     # yanchor =  'top'  #reposition title
                     ),
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     # range = as.Date(c(plotStartRange,plotEndRange)),
                     rangeselector = list(
                       buttons = list(
                          list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )#,
                       # x = 0.6,           #put rangeselector on right side
                       # xanchor = "left"   #put rangeselector on right side
                     ),
                     #for dates on x-axis, this worked: tickmode = linear and set both tick0/dtick
                     #for % on y-axis, this worked: tickmode = array and set both tickvals/ticktext
                     #h/t: https://stackoverflow.com/questions/68475195/dticks-and-plotly-how-to-control-what-is-shown-on-x-axes
                     tickmode = 'linear', 
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y' #added this b/c tick labels formatted with ggplot were being cutoff by graph, this allows correct alignment and spacing
                     )#,   
        #to customize both range and # of tick labels, use this instead of the above
        #https://plotly.com/r/time-series/
        #h/t: https://stackoverflow.com/questions/71823559/how-to-set-custom-date-ticks-breaks-in-plotly
        # yaxis = list(range = c(-0.05,1.05), #changed from 0,1 to -.05,1.05 to add small margin/padding at ends of graph
        #              autorange = FALSE,
        #              tickmode = 'array',
        #              tickvals = seq(0,1,.1),
        #              ticktext = paste0(seq(0,100,10),'%'))
             ) %>%
      # rangeslider(type = 'date', start = min(case_dispo_df2$trial_week) - 7, end = max(case_dispo_df2$trial_week) + 7, thickness = .1) %>% # use +/- 7 to add some padding to left and right side of plot and rangeslider
  rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

```

## Weekly and Cumulative Deferrals by Division

```{r}
#| echo: false
#| warning: false
#| message: false

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(gghighlight)
library(ggtext)

choicesCaseDispoSelect <- case_dispo_df2 %>% 
  select(Division) %>% 
  distinct() %>% 
  filter(Division != "All Divisions") %>% 
  arrange(Division) %>% 
  pull()

# selectizeInput(inputId = "caseDispoSelect",
#                label = "Select Division:",
#                choices = choicesCaseDispoSelect,
#                selected = choicesCaseDispoSelect[1],
#                multiple = TRUE
#                )

selectizeInput(inputId = "caseDispoSelect",
               label = "Select Division:",
               choices = choicesCaseDispoSelect,
               selected = choicesCaseDispoSelect[1],
               multiple = FALSE
               )

plotlyOutput("gg_deferrals_divs", height = 600)

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(tidyr)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_deferral_stats_1C_trial_week_ to dispo_case_trial_stats_1C_trial_week_)
csv_deferral_list <- list.files("WeeklyData/", pattern = "^dispo_charge_deferral_stats_1C_trial_week_.*csv$")
csv_deferral_list <- csv_deferral_list[-length(csv_deferral_list)]

charge_deferral_list <- lapply(paste0("WeeklyData/", csv_deferral_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_deferral_df <- bind_rows(setNames(charge_deferral_list, basename(csv_deferral_list)), .id = "id") #bind_rows(case_dispo_list)

charge_deferral_division <- charge_deferral_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)",  "1C23 (Somerville)", "All Divisions"))) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Weekly Deferrals` = Total,
         `Total Successful` = cumsum(Successful),
         `Total Unsuccessful` = cumsum(Unsuccessful),
         `Total Deferrals` = cumsum(Total)) %>%   
  ungroup()

yaxis_lims_deferrals <- charge_deferral_df %>% 
    mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
           Division = if_else(Division == "-", "All Divisions", Division),
           Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                             labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions"))) %>% 
    filter(Division != "All Divisions") %>%
    group_by(Judge) %>% 
    summarize(total_deferrals = sum(Total)) %>% 
    ungroup() %>%
  filter(Judge != "Total")

ymax_deferrals <- max(yaxis_lims_deferrals$total_deferrals) + 1

charge_deferrals_division_long <- charge_deferral_division %>% pivot_longer(cols = c(`Weekly Deferrals`, `Total Successful`:`Total Deferrals`), values_to = "Deferrals", names_to = "Type") 

charge_deferrals_division_long$Type <- factor(charge_deferrals_division_long$Type, levels = c("Weekly Deferrals", "Total Deferrals", "Total Successful", "Total Unsuccessful"))

charge_deferrals_division_line <- subset(charge_deferrals_division_long, Type != "Weekly Deferrals") %>% filter(Division != "All Divisions")
charge_deferrals_division_bar <- subset(charge_deferrals_division_long, Type == "Weekly Deferrals") %>% filter(Division != "All Divisions")

  charge_deferrals_df2 <- reactive({charge_deferrals_division_line %>% 
    group_by(Division, cyear) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})

    charge_deferrals_bar <- reactive({charge_deferrals_division_bar %>% 
    group_by(Division, cyear) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})

output$gg_deferrals_divs <- renderPlotly({
  
  gg_deferrals_divs <- ggplot(charge_deferrals_df2(),
                          aes(x = trial_week, y = Deferrals, group = Type, colour = Type,
                              text = paste0("week: ",trial_week,"\n",
                                            "cumulative # of deferrals:", Deferrals, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
      geom_col(charge_deferrals_bar(), 
             fill = "#FFFFFF", 
             mapping = aes(x = trial_week, y = Deferrals, group = Type, 
                           text = paste0("week: ",trial_week, "\n",
                                             "Weekly Deferrals: ", Deferrals, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
    geom_point() +
    geom_line() +
scale_color_manual(values=c("#000000", "#0000FF", "#00FF00", "#FF0000")) +
    #ISSUE: the x-axis was showing an extra label on each end of plot, tried a few methods to fix this
    # scale_x_date("Week", date_breaks = "1 week") +
    # scale_x_date(date_breaks = "1 week", date_labels = "%m-%d-%y") +
    scale_x_date(breaks = seq(as.Date("2024-01-01"), max(charge_deferrals_df2()$trial_week), by = 7), date_labels = "%m-%d-%y") +
    #ISSUE: for judges with 0 or few trials, the y-axis has non-integer values, looks bad, use method 1 as a fix:
    #method 0:
    # scale_y_continuous(limits = c(0,NA)) +
    #method 1:
    scale_y_continuous(limits = c(0, ymax_deferrals)) +
    #method 2:
    # scale_y_continuous(breaks = seq(0, sum(case_dispo_df2()$Total) + 1, by = 5)) +
    # scale_y_continuous("Total Pending Trials") +
    # scale_color_discrete("Divisions") +
    labs(title = paste0("Weekly and Cumulative Deferrals in ", input$caseDispoSelect),
         x = NULL,
         y = "Number of Deferrals",
         color = "Divisions") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 30)) +
         NULL

ggplotly(gg_deferrals_divs,tooltip = "text", dynamicTicks = TRUE) %>%
      # hide_legend() %>%
      layout(
        #moved title and subtitle to the shinydashboard box b/c it didn't format nicely with selectorbuttons, especially on smaller screens
        # title = list(text=paste0('Weekly and Cumulative Trials (All Divisions)')
        #              # xanchor = 'left', #reposition title
        #              # yanchor =  'top'  #reposition title
        #              ),
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     # range = as.Date(c(plotStartRange,plotEndRange)),
                     rangeselector = list(
                       buttons = list(
                         list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )#,
                       # x = 0.6,           #put rangeselector on right side
                       # xanchor = "left"   #put rangeselector on right side
                     ),
                     #for dates on x-axis, this worked: tickmode = linear and set both tick0/dtick
                     #for % on y-axis, this worked: tickmode = array and set both tickvals/ticktext
                     #h/t: https://stackoverflow.com/questions/68475195/dticks-and-plotly-how-to-control-what-is-shown-on-x-axes
                     tickmode = 'linear', 
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y' #added this b/c tick labels formatted with ggplot were being cutoff by graph, this allows correct alignment and spacing
                     ),   
        #to customize both range and # of tick labels, use this instead of the above
        #https://plotly.com/r/time-series/
        #h/t: https://stackoverflow.com/questions/71823559/how-to-set-custom-date-ticks-breaks-in-plotly
        # yaxis = list(range = c(-0.05,1.05), #changed from 0,1 to -.05,1.05 to add small margin/padding at ends of graph
        #              autorange = FALSE,
        #              tickmode = 'array',
        #              tickvals = seq(0,1,.1),
        #              ticktext = paste0(seq(0,100,10),'%'))
          yaxis = list(autorange = FALSE)
             ) %>%

      # rangeslider(type = 'date', start = min(case_dispo_df2()$trial_week) - 7, end = max(case_dispo_df2()$trial_week) + 7, thickness = .1) %>% # use +/- 7 to add some padding to left and right side of plot and rangeslider
      rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

})
```

# Probation Dispositions (`r title` Level)

## Weekly Probation Table

The table below shows the number of probation revocations and dismissals across each criminal division in the First Circuit, Circuit Court. Use the drop down to look at historical weekly reports.

```{r}
#| echo: false
#| warning: false
#| message: false
library(dplyr)
library(stringr)
library(shiny)
library(htmltools)
library(DT)
library(ggtext)


csv_probation_list <- list.files("WeeklyData/", pattern = "^dispo_charge_probation_stats_1C_trial_week_.*csv$")
run_dates_probation <- str_extract(csv_probation_list, "[0-9]{4}-[0-9]{2}-[0-9]{2}")
run_dates_aggregate <- str_extract(csv_probation_list, "Aggregate")
run_dates_probation <- append(run_dates_probation,run_dates_aggregate)
run_dates_probation <- run_dates_probation[!is.na(run_dates_probation)]

selectizeInput(inputId = "selectWeekDispo_Probation",
               label = "Select a report:",
               choices = rev(run_dates_probation),
               selected = TRUE)

DTOutput("probation_table")

#attempt to add download button using just shiny widgets to save table displayed with Kable
# downloadButton(outputId = "saveCSV", label = "CSV")

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(kableExtra)
library(DT)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_probation_stats_1C_trial_week_ to dispo_casee_probation_stats_1C_trial_week_)

weekly_probation_table <- reactive({
    csv_selected <- list.files("WeeklyData/", pattern = paste0("^dispo_charge_probation_stats_1C_trial_week_", input$selectWeekDispo_Probation,".*?csv$"))
  dispo_trial_table_full <- read.csv(file = paste0("WeeklyData/", csv_selected))
  dispo_trial_table_full %>% rename(
    `First Revocation` = FirstRevocation,
    `Second Revocation` = SecondRevocation,
    `> 2 Revocations` = MoreThanTwo)
  })

output$probation_table <- renderDT(
  weekly_probation_table(), 
  rownames = F,
  # colnames = c("Trial week", "1C01 (Wong)", "1C02 (Remigio)", "1C03 (Ho)", "1C11 (Souza)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C22 (Park)", "1C23 (Somerville)", "Total"),
    # colnames = c("Judge\n","Division","JRT","JWT","COP","DSM","DWO","DPJ","NPQ","RMD","MISC","Total"),
    extensions = c("Buttons", "FixedColumns"),
    options = list(
      pageLength = 15,
      # lengthMenu = c(15, 25, 50),
      # scrollY = "600px", #this was creating some weird behavior in which the column heads of previous table were partially appearing
      scrollX = TRUE,
      #add buttons, and specifying dom
      #https://stackoverflow.com/questions/50039186/add-download-buttons-in-dtrenderdatatable
      #https://stackoverflow.com/questions/50043152/r-shiny-how-to-add-pagination-in-dtrenderdatatable
      # dom = 'Bfrtip',
      dom = 'tB',
      buttons = c('copy','csv','excel','pdf'),
      fixedColumns = list(leftColumns = 1)  # Freeze first column
      # h/t: customize font size of column heads: https://github.com/rstudio/DT/issues/783
      # headerCallback = DT::JS(
      #   "function(thead) {",
      #   "  $(thead).css('font-size', '14px');",
      #   "}"
      #   )
    )
)

```

## Weekly and Cumulative Probation Dispositions

```{r}
#| echo: false
#| warning: false
#| message: false

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_probation_stats_1C_trial_week_ to dispo_casee_probation_stats_1C_trial_week_)
csv_charge_probation_list <- list.files("WeeklyData/", pattern = "^dispo_charge_probation_stats_1C_trial_week_.*csv$")
csv_charge_probation_list <- csv_charge_probation_list[-length(csv_charge_probation_list)]

charge_probation_list <- lapply(paste0("WeeklyData/", csv_charge_probation_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_probation_df <- bind_rows(setNames(charge_probation_list, basename(csv_charge_probation_list)), .id = "id") #bind_rows(case_dispo_list)

  charge_probation_cumulative <- charge_probation_df %>% 
    mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
           cyear = format(trial_week, "%Y"),
           Division = if_else(Division == "-", "All Divisions", Division),
           Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                             labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
           `Weekly Probation Dispositions` = Revocations + Dismissals   
    ) %>% 
    group_by(Division, cyear) %>%   
    mutate(`Total Dispositions` = cumsum(Total),
           `Revocations` = cumsum(Revocations),
           `Dismissals` = cumsum(Dismissals)) %>% 
    ungroup()  
  
case_probation_aggregate_long <- charge_probation_cumulative %>% pivot_longer(cols = c(Revocations,`Weekly Probation Dispositions`,`Total Dispositions`), names_to = "Type", values_to = "Probation Dispositions")

case_probation_aggregate_long$Type <- factor(case_probation_aggregate_long$Type, levels = c("Total Dispositions", "Revocations", "Weekly Probation Dispositions"))

cumulative_probation_line <- subset(case_probation_aggregate_long, Type != "Weekly Probation Dispositions") %>% filter(Division == "All Divisions")
weekly_probation_bar <- subset(case_probation_aggregate_long, Type == "Weekly Probation Dispositions") %>% filter(Division == "All Divisions")

gg_probation_all <- ggplot(cumulative_probation_line %>% filter(Division == "All Divisions"),
                          aes(x = trial_week, y = `Probation Dispositions`, colour = Type, group = Type,
                              text = paste0("week: ",trial_week,"\n",
                                            "# of dispositions: ", `Probation Dispositions`, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
  geom_point() +
  geom_line() +
  geom_col(data = weekly_probation_bar,fill = "#FFFFFF", aes(x = trial_week, y = `Probation Dispositions`, group =  Type)) +
  scale_color_manual(values=c("#0000FF","#FF0000", "#000000")) +
  scale_x_date(breaks = seq(as.Date("2024-01-01"), max(charge_probation_cumulative$trial_week), by = 7), date_labels = "%m-%d-%y") +
  scale_y_continuous(limits = c(0,NA)) +
  labs(title = "Weekly and Cumulative Probation Revocations/Dismissals (All Divisions)",
       x = NULL,
       y = "Number of dispositions",
       color = NULL) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 30))+
  NULL

ggplotly(gg_probation_all, tooltip = "text", dynamicTicks = TRUE) %>%
      layout(
        title = list(text=paste0('Weekly and Cumulative Probation Dispos (All Divisions)')
                     ),
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     rangeselector = list(
                       buttons = list(
                          list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )
                     ),
                     #for dates on x-axis, this worked: tickmode = linear and set both tick0/dtick
                     #for % on y-axis, this worked: tickmode = array and set both tickvals/ticktext
                     #h/t: https://stackoverflow.com/questions/68475195/dticks-and-plotly-how-to-control-what-is-shown-on-x-axes
                     tickmode = 'linear', 
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y' #added this b/c tick labels formatted with ggplot were being cutoff by graph, this allows correct alignment and spacing
                     )#,   
        #to customize both range and # of tick labels, use this instead of the above
        #https://plotly.com/r/time-series/
        #h/t: https://stackoverflow.com/questions/71823559/how-to-set-custom-date-ticks-breaks-in-plotly
        # yaxis = list(range = c(-0.05,1.05), #changed from 0,1 to -.05,1.05 to add small margin/padding at ends of graph
        #              autorange = FALSE,
        #              tickmode = 'array',
        #              tickvals = seq(0,1,.1),
        #              ticktext = paste0(seq(0,100,10),'%'))
             ) %>%
      # rangeslider(type = 'date', start = min(case_dispo_df2$trial_week) - 7, end = max(case_dispo_df2$trial_week) + 7, thickness = .1) %>% # use +/- 7 to add some padding to left and right side of plot and rangeslider
  rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

```

## Probation Trends By Division

```{r}
#| echo: false
#| warning: false
#| message: false

library(shiny)
library(ggplot2)
library(dplyr)
library(stringr)
library(plotly)

plotOutput("facet_probation", height = 1200) 

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_probation_stats_1C_trial_week_ to dispo_casee_probation_stats_1C_trial_week_)
csv_charge_probation_list <- list.files("WeeklyData/", pattern = "^dispo_charge_probation_stats_1C_trial_week_.*csv$")
csv_charge_probation_list <- csv_charge_probation_list[-length(csv_charge_probation_list)]

  charge_probation_list <- lapply(paste0("WeeklyData/", csv_charge_probation_list), read.csv)
  
  case_probation_df <- bind_rows(setNames(charge_probation_list, basename(csv_charge_probation_list)), .id = "id") #bind_rows(case_dispo_list)
  
  case_probation_division <- case_probation_df %>% 
    mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
           cyear = format(trial_week, "%Y"),
           Division = if_else(Division == "-", "All Divisions", Division),
           Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                             labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)", "1C23 (Somerville)", "All Divisions")),
           `Weekly Probation Dispositions` = Revocations + Dismissals   
    ) %>% 
    group_by(Division, cyear) %>%   
    mutate(`Total Dispositions` = cumsum(Total),
           `Revocations` = cumsum(Revocations),
           `Dismissals` = cumsum(Dismissals)) %>% 
    ungroup()  
  
   #df by month
    case_probation_division_month <- case_probation_division %>%
      mutate(period = floor_date(trial_week, "month")) %>%
      group_by(period, Division) %>%
      summarize(total_dispositions = sum(`Weekly Probation Dispositions`), .groups = "drop")
  
    #monthly facet graph
     # case_deferral_division_month %>% filter(Division != "All Divisions") %>% ggplot(aes(x = period, y = total_dispositions, group = Division, color = Division)) + 
     # geom_col(aes(fill = Division)) + 
     # facet_wrap(vars(class = Division)) +
     # labs(x = NULL) +
     # theme_bw() +
     # theme(strip.text.x = element_text(size = 25, face = "bold"), 
     #       legend.position="none",
     #       axis.text.x.bottom = element_text(size = 18),
     #       axis.text.y.left = element_text(size = 18),
     #       axis.title.y = element_text(size = 25, face = "bold")
     #       ) + 
     #   scale_x_date(breaks = "1 month", date_labels = "%b")
     # 
  
  output$facet_probation <- renderPlot({
  case_probation_division %>% filter(Division != "All Divisions") %>% ggplot(aes(x = trial_week, y = `Total Dispositions`, group = Division, color = Division)) +     
    geom_col(aes(fill = Division)) + 
    facet_wrap(vars(class = Division)) +
    labs(x = NULL) +
    theme_bw() +
    theme(strip.text.x = element_text(size = 25, face = "bold"), 
          legend.position="none",
          axis.text.x.bottom = element_text(size = 18),
          axis.text.y.left = element_text(size = 18),
          axis.title.y = element_text(size = 25, face = "bold")
          ) #+ 
      #scale_y_continuous(limits = c(0,15))
    } 
  ) 
```


## Weekly Probation Trends by Division

```{r}
#| echo: false
#| warning: false
#| message: false

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(gghighlight)
library(ggtext)

choicesCaseDispoSelect <- case_dispo_df2 %>% 
  select(Division) %>% 
  distinct() %>% 
  filter(Division != "All Divisions") %>% 
  arrange(Division) %>% 
  pull()

# selectizeInput(inputId = "caseDispoSelect",
#                label = "Select Division:",
#                choices = choicesCaseDispoSelect,
#                selected = choicesCaseDispoSelect[1],
#                multiple = TRUE
#                )

selectizeInput(inputId = "caseDispoSelect",
               label = "Select Division:",
               choices = choicesCaseDispoSelect,
               selected = choicesCaseDispoSelect[1],
               multiple = FALSE
               )

plotlyOutput("gg_probation_divs", height = 600)

```

```{r}
#| echo: false
#| warning: false
#| message: false
#| context: server

library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(tidyr)

#ALERT: TOGGLE CHARGE TO CASE (dispo_charge_probation_stats_1C_trial_week_ to dispo_casee_probation_stats_1C_trial_week_)
csv_charge_probation_list <- list.files("WeeklyData/", pattern = "^dispo_charge_probation_stats_1C_trial_week_.*csv$")
csv_charge_probation_list <- csv_charge_probation_list[-length(csv_charge_probation_list)]

charge_probation_list <- lapply(paste0("WeeklyData/", csv_charge_probation_list), read.csv)
# h/t: https://stackoverflow.com/questions/75190497/add-filename-as-an-attribute-while-reading-multiple-csv-w-lapply-or-add-filena
charge_probation_df <- bind_rows(setNames(charge_probation_list, basename(csv_charge_probation_list)), .id = "id") #bind_rows(case_dispo_list)

charge_probation_division <- charge_probation_df %>% 
  mutate(trial_week = as.Date(str_extract(id, "[0-9]{4}-[0-9]{2}-[0-9]{2}")),
         cyear = format(trial_week, "%Y"),
         Division = if_else(Division == "-", "All Divisions", Division),
         Division = factor(Division, levels = c("1", "2", "6", "11", "13", "15", "17", "19", "20", "21",  "23", "All Divisions"),
                           labels = c("1C01 (Wong)", "1C02 (Remigio)", "1C06 (Costa)", "1C11 (Souza)", "1C13 (Viola)", "1C15 (Malinao)", "1C17 (Johnson)", "1C19 (To'oto'o)", "1C20 (Morikawa)", "1C21 (Kawashima)",  "1C23 (Somerville)", "All Divisions"))) %>% 
  group_by(Division, cyear) %>% 
  mutate(`Weekly Probation Dispositions` = Total,
         `Total Revocations` = cumsum(Revocations),
         `Total Dismissals` = cumsum(Dismissals),
         `Total Probation Dispositions` = cumsum(Total)) %>%   
  ungroup()

yaxis_lims_probation <- charge_probation_division %>% 
    filter(Division != "All Divisions") %>%
    group_by(Judge) %>% 
    summarize(total_probation = sum(Total)) %>% 
    ungroup() %>%
  filter(Judge != "Total")

ymax_probation <- max(yaxis_lims_probation$total_probation) + 1

charge_probation_division_long <- charge_probation_division %>% pivot_longer(cols = c(`Weekly Probation Dispositions`, `Total Revocations`,`Total Probation Dispositions`), values_to = "Probation", names_to = "Type") 

charge_probation_division_long$Type <- factor(charge_probation_division_long$Type, levels = c("Weekly Probation Dispositions", "Total Probation Dispositions", "Total Revocations"))

charge_probation_division_line <- subset(charge_probation_division_long, Type != "Weekly Probation Dispositions") %>% filter(Division != "All Divisions")
charge_probation_division_bar <- subset(charge_probation_division_long, Type == "Weekly Probation Dispositions") %>% filter(Division != "All Divisions")

  charge_probation_df2 <- reactive({charge_probation_division_line %>% 
    group_by(Division, cyear) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})

    charge_probation_bar <- reactive({charge_probation_division_bar %>% 
    group_by(Division, cyear) %>% 
    ungroup() %>%
    filter(Division %in% input$caseDispoSelect)
})

output$gg_probation_divs <- renderPlotly({
  
  gg_probation_divs <- ggplot(charge_probation_df2(),
                          aes(x = trial_week, y = Probation, group = Type, colour = Type,
                              text = paste0("week: ",trial_week,"\n",
                                            "cumulative # of deferrals:", Probation, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
      geom_col(charge_probation_bar(), 
             fill = "#FFFFFF", 
             mapping = aes(x = trial_week, y = Probation, group = Type, 
                           text = paste0("week: ",trial_week, "\n",
                                             "Weekly Probation: ", Probation, "\n",
                                            "division: ", Division, "\n",
                                            "year: ", cyear))) +
    geom_point() +
    geom_line() +
scale_color_manual(values=c("#000000","#0000FF",  "#FF0000")) +
    #ISSUE: the x-axis was showing an extra label on each end of plot, tried a few methods to fix this
    # scale_x_date("Week", date_breaks = "1 week") +
    # scale_x_date(date_breaks = "1 week", date_labels = "%m-%d-%y") +
    scale_x_date(breaks = seq(as.Date("2024-01-01"), max(charge_deferrals_df2()$trial_week), by = 7), date_labels = "%m-%d-%y") +
    #ISSUE: for judges with 0 or few trials, the y-axis has non-integer values, looks bad, use method 1 as a fix:
    #method 0:
    # scale_y_continuous(limits = c(0,NA)) +
    #method 1:
    scale_y_continuous(limits = c(0, ymax_probation)) +
    #method 2:
    # scale_y_continuous(breaks = seq(0, sum(case_dispo_df2()$Total) + 1, by = 5)) +
    # scale_y_continuous("Total Pending Trials") +
    # scale_color_discrete("Divisions") +
    labs(title = paste0("Weekly and Cumulative Deferrals in ", input$caseDispoSelect),
         x = NULL,
         y = "Number of Deferrals",
         color = "Divisions") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 30)) +
         NULL

ggplotly(gg_probation_divs,tooltip = "text", dynamicTicks = TRUE) %>%
      # hide_legend() %>%
      layout(
        #moved title and subtitle to the shinydashboard box b/c it didn't format nicely with selectorbuttons, especially on smaller screens
        # title = list(text=paste0('Weekly and Cumulative Trials (All Divisions)')
        #              # xanchor = 'left', #reposition title
        #              # yanchor =  'top'  #reposition title
        #              ),
        margin = list(t = 90),
        xaxis = list(type = 'date',
                     autorange = FALSE,
                     # range = as.Date(c(plotStartRange,plotEndRange)),
                     rangeselector = list(
                       buttons = list(
                         list(count=3, label="3m", step="month", stepmode="backward"),
                         list(count=6, label="6m", step="month", stepmode="backward"),
                         list(count=1, label="YTD", step="year", stepmode="todate"),
                         list(count=1, label="1y", step="year", stepmode="backward"),
                         list(count=2, label="2y", step="year", stepmode="backward"),
                         list(step="all")
                       )#,
                       # x = 0.6,           #put rangeselector on right side
                       # xanchor = "left"   #put rangeselector on right side
                     ),
                     #for dates on x-axis, this worked: tickmode = linear and set both tick0/dtick
                     #for % on y-axis, this worked: tickmode = array and set both tickvals/ticktext
                     #h/t: https://stackoverflow.com/questions/68475195/dticks-and-plotly-how-to-control-what-is-shown-on-x-axes
                     tickmode = 'linear', 
                     tick0 = plotStartRange,
                     dtick = 'M1',
                     tickformat = '%b %Y' #added this b/c tick labels formatted with ggplot were being cutoff by graph, this allows correct alignment and spacing
                     ),   
        #to customize both range and # of tick labels, use this instead of the above
        #https://plotly.com/r/time-series/
        #h/t: https://stackoverflow.com/questions/71823559/how-to-set-custom-date-ticks-breaks-in-plotly
        # yaxis = list(range = c(-0.05,1.05), #changed from 0,1 to -.05,1.05 to add small margin/padding at ends of graph
        #              autorange = FALSE,
        #              tickmode = 'array',
        #              tickvals = seq(0,1,.1),
        #              ticktext = paste0(seq(0,100,10),'%'))
          yaxis = list(autorange = FALSE)
             ) %>%

      # rangeslider(type = 'date', start = min(case_dispo_df2()$trial_week) - 7, end = max(case_dispo_df2()$trial_week) + 7, thickness = .1) %>% # use +/- 7 to add some padding to left and right side of plot and rangeslider
      rangeslider(type = 'date', start = plotStartRange, end = plotEndRange, thickness = .1) %>%
  config(modeBarButtonsToRemove = c('hoverClosestCartesian','hoverCompareCartesian'), displaylogo = FALSE)

})
```